Syntax Is All You Need: A Universal-Language Approach to Mutant Generation

### 2023-03-29 paper/main.tex
starter table for java vs others

\begin{table}[hbtp]
\centering
\caption{Rust (Regex vs. Comby)}
\label{tab:table_rust1}
\resizebox{\columnwidth}{!}{%
\begin{tabular}{|c|c|c|r|r|r|c|}
\hline
 & \multicolumn{2}{c|}{} & \textbf{Valid} & \textbf{Invalid} & \textbf{Valid \%} &  \textbf{LOC} \\ \hline
\multirow{2}{*}{cargo release} & \multicolumn{2}{c|}{Regex} & 851 \hspace{8pt} &	1163 \hspace{8pt} & 42.25\%  & \multirow{2}{*}{346}\\\cline{2-6}
    & \multicolumn{2}{c|}{Comby} & 1690 \hspace{8pt} & 711 \hspace{8pt} & 70.39\% & \\ \hline
\multirow{2}{*}{passerine} & \multicolumn{2}{c|}{Regex} & 213 \hspace{8pt} & 2081 \hspace{8pt} & 9.29\% & \multirow{2}{*}{376}\\\cline{2-6}
    & \multicolumn{2}{c|}{Comby} & 173 \hspace{8pt} & 1518 \hspace{8pt} & 10.23\% & \\ \hline
\multirow{2}{*}{typos} & \multicolumn{2}{c|}{Regex} & 386 \hspace{8pt} & 1534 \hspace{8pt} & 20.10\% & \multirow{2}{*}{463}\\\cline{2-6}
    & \multicolumn{2}{c|}{Comby} & 366 \hspace{8pt} & 1199 \hspace{8pt} &	 23.39\% & \\ \hline

 & \multirow{3}{*}{Comby} & Mean & 554.00 & 1055.83	& 29.29\% & \\\cline{3-6}
    &   &  Median & 384.00 & 1059.50	& 25.60\%  & \\\cline{3-6}
    &   &  Std. Dev & 592.63 & 508.30 & 21.63\%  & \\\hline
\end{tabular}

@@

% ---------------- C++ table (UM vs Others)--------------------------
\begin{table}[htbp]
\centering
{\small
\caption{C++ (Our Implementation vs. Dextool)}
\label{tab:table_cpp2}
\begin{tabularx}{\columnwidth}{X|crr|crr}
\hline
        & \multicolumn{3}{c|}{Comby}  & \multicolumn{3}{c}{Dextool} \\ 
Project & Mutants & \makecell{\textbf{Mut.} \\ \textbf{Score}} & \textbf{\% Eqv.} & $\frac{killed}{total}$ & \makecell{\textbf{Mut.} \\ \textbf{Score}} & \textbf{\% Eqv.} \\[1ex]\midrule
 ompl &  564 & 0.07 & 40\% & 278 & 0.08 & N/A \\
%\multirow{3}{*}{\small libgraphqlparser} & Comby & 116 & 15 & 0.89 & 20\% \\ \cline{2-6}
%    & Dextool & 50 & 2 & 0.96 & N/A \\ \hline
%\multirow{3}{*}{\small rethinkdb\_rebirth} & Comby & 49 & 443 & 0.10 & 20\% \\ \cline{2-6}
%    & Dextool & 9 & 16 & 0.36 & N/A \\ \hline

@@

>>>>

@@

% ---------------- C++ table (UM vs Others)--------------------------
\begin{table}[htbp]
\centering
{\small
\caption{C++ (Our Implementation vs. Dextool)}
\label{tab:table_cpp2}
\begin{tabularx}{\columnwidth}{X|crr|crr}
\hline
        & \multicolumn{3}{c|}{Comby}  & \multicolumn{3}{c}{Dextool} \\ 
Project & Mutants & \makecell{\textbf{Mut.} \\ \textbf{Score}} & \textbf{\% Eqv.} & Mutants & \makecell{\textbf{Mut.} \\ \textbf{Score}} & \textbf{\% Eqv.} \\[1ex]\midrule
 ompl &  564 & 0.07 & 40\% & 278 & 0.08 & N/A \\
%\multirow{3}{*}{\small libgraphqlparser} & Comby & 116 & 15 & 0.89 & 20\% \\ \cline{2-6}
%    & Dextool & 50 & 2 & 0.96 & N/A \\ \hline
%\multirow{3}{*}{\small rethinkdb\_rebirth} & Comby & 49 & 443 & 0.10 & 20\% \\ \cline{2-6}
%    & Dextool & 9 & 16 & 0.36 & N/A \\ \hline

@@

\begin{table}[htbp]
\centering
{\small
\caption{Java (Our Implementation vs. PIT vs. LittleDarwin)}
\label{tab:table_java2}
\begin{tabularx}{\columnwidth}{l|rrr|rrr|rrr}
\hline
                 & \mc{3}{c|}{Comby}   & \mc{3}{c|}{PIT} & \mc{3}{c}{LittleDarwin} \\
\textbf{Project} & \textbf{Mutants} &  \makecell{\textbf{Mutation} \\ \textbf{Score}} & \textbf{\% Eqv}
& \textbf{Mutants} &  \makecell{\textbf{Mutation} \\ \textbf{Score}} & \textbf{\% Eqv} 
& \textbf{Mutants} &  \makecell{\textbf{Mutation} \\ \textbf{Score}} & \textbf{\% Eqv} \\ \midrule

pebble & 85 & 0.81 & 50\% & 20 & 0.95 & N/A & 8 & 1.00 0\% \\
... \\\midrule
\textbf{Mean} &  XX & XX & XX & XX & XX & XX & XX & XX & XX \\
\textbf{Std.Dev.} &  XX & XX & XX & XX & XX & XX & XX & XX & XX \\
\end{tabularx}
}
\end{table}
